\documentclass[twocolumn,showpacs,showkeys,prd,superscriptaddress]{revtex4-1}

\usepackage{float}
\usepackage{subfigure}
\usepackage{siunitx}
\usepackage{ragged2e}

%%%%%%%%% CORRECTIONS %%%%%%%%%
\usepackage{ulem}
\newcommand\pro[1]{{\color{blue}#1}}
\newcommand\out[1]{{\color{red}\sout{#1}}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{definitions}
\input{tikzdefinitions}


\begin{document}
%\title{Torsional Contribution to One-Loop Observables in an Effective Theory Coming From Extra Dimensions}
\title{Torsion in Extra Dimensions and One-Loop Observables}

\author{Crist\'obal \surname{Corral}}
\email{cristobal.corral@postgrado.usm.cl}
\affiliation{Departamento de F\'\i sica, Universidad T\'ecnica Federico Santa Mar\'\i a, Casilla 110-V, Valpara\'\i so, Chile.}

\author{Oscar \surname{Castillo-Felisola}}
\email{o.castillo.felisola@gmail.com} 
\affiliation{Departamento de F\'\i sica, Universidad T\'ecnica Federico Santa Mar\'\i a, Casilla 110-V, Valpara\'\i so, Chile.}
\affiliation{Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Chile.}

\author{Sergey \surname{Kovalenko}}
\email{sergey.kovalenko@usm.cl}  
\affiliation{Departamento de F\'\i sica, Universidad T\'ecnica Federico Santa Mar\'\i a, Casilla 110-V, Valpara\'\i so, Chile.}
\affiliation{Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Chile.}

\author{Iv\'an \surname{Schmidt}}
\email{ivan.schmidt@usm.cl}  
\affiliation{Departamento de F\'\i sica, Universidad T\'ecnica Federico Santa Mar\'\i a, Casilla 110-V, Valpara\'\i so, Chile.}
\affiliation{Centro Cient\'ifico Tecnol\'ogico de Valpara\'iso, Chile.}

\begin{abstract}
  \out{In the present work, Cartan-Einstein formulation of gravity in extra dimension scenario have been considered. Non zero torsion have been included by considering gravity coupled with fermions in the minimal extension of this theory. This consideration gives origin to a four fermion interaction in a natural way.}
  The aim of this article is to explore one-loop observables due the four fermion interaction in a effective theory coming from the torsionful extra dimension scenario. The results are compared with Standard Model precision tests, allowing  to constraint the scale for new physics and the parameters of the model.
\end{abstract}

\maketitle


\input{introduction}
\input{einsteincartan}
\input{extradim}
\input{oneloop}
\input{constraints}
\input{conclusions}
\input{acknowledgement}

\appendix

\input{apendix1}

\bibliographystyle{unsrt}
\bibliography{bibliography}

\end{document}
