\section{\label{sec:conclusions}Conclusions}

In the present work a more general formulation of Gravity has been consider: the Cartan-Einstein Formalism. This framework gives rise to a contact four fermion interaction from the equations of motion, that is highly suppressed by the inverse of the squared Planck mass in $4$-dimensions. 

In order to deal with this, an scenario without this hierarchy between gravitational and SM interactions has been used: RS model \cite{Randall:1999ee}. This model suggests the existence of one large extra dimension and the hierarchy between the fundamental ($5$-dimensional) and the effective ($4$-dimensional) Planck mass is an exponential function. However, in order to deal with $4$-dimensional observables, this large extra dimension is compactified on an orbifold $S^1/\mathbb{Z}_2$ of radius $R$. This compactification leads to an effective theory in $4$-dimensions with a four fermion interaction due torsion. 

Considering this four fermion interaction in RS scenario, it can be decomposed in two terms: an axial-vector and axial-tensor interaction. By geometrical reasons of the present model this last term vanishes and leads only to the axial-vector one. One of the phenomenological implication of this absence is that the torsion contributions to observables like leptonic anomalous magnetic moment are forbidden. 

Although this axial-tensor interaction does not appears in the effective theory one can explore axial-vector mediated observables as $Z^0$ boson width decay at one-loop level. In Sec.~\ref{sec:oneloop} form factors are obtained from neutral bosons exchange processes. Using these form factors and the calculation of $Z^0$ boson width decay, the scale for new physics coming from torsionful extra dimension scenario has been achieved. The use of SM presicion tests data leads to a scale for new physics $ \Lambda \geq 53.9364\;[\text{TeV}]$ which constraints strongly the parameters of this theory, for different fermion localization values, as Eq.~\eqref{parconst} shown.
